Risk and Trust in Open Systems:\\ \Large Towards formalising Permission and Authority, and specifying policies for Object Capability Patterns

### 2017-09-08 shupeng_msc_report.tex
final

From the contraposition of the our observation previously that [Permission is necessary for Authority], we have the corollary:\\

\begin{logic}
\hr\\
\emp{Isolation implies no authority}\\
M,\losigma\ \loturns\ \loneg MayAccess$^{Ind,Eve}$(o,o$'$) \loimplies\ M,\losigma\ \loturns\ \loneg Maycall(o,o$'$)\\
\hr
\end{logic}

@@

We provide some analogies as to why cooperation does not imply authority. Object o can have the reference(capability) of o$'$, and hence there is cooperation, but o contains no methods that can invoke(use) the capability of o$'$, and thus o has the capability of o$'$ but not the authority of o$'$. Another analogy, from the other viewpoint of o$'$, would be that o$'$ has no available methods that can be invoked by o ---this can happen if o has no methods, or o only contains private methods or methods that are restricted for objects inherited from the same class as o of which o$'$ is not.\\

@@

This says that if we have a configuration where object o$'$ is dominated by known objects, then the permission to use o$'$ by o* must involve at least a trusted object s$'$. Therefore we can allow cooperation between o* and o$'$, and still make it safe by using an attenuating trusted object to \textit{shift the vulnerability} from the object of interest o$'$ to the attenuating trusted object. This shows that we can use attenuating objects to implement cooperation without vulnerability (of the object of interest) in OCap systems.\\

>>>>

From the contraposition of the observation previously that [Permission is necessary for Authority], we have another observation:\\

\begin{logic}
\hr\\
\emp{Observation---[Isolation implies no authority]}\\
M,\losigma\ \loturns\ \loneg MayAccess$^{Ind,Eve}$(o,o$'$) \loimplies\ M,\losigma\ \loturns\ \loneg Maycall(o,o$'$)\\
\hr
\end{logic}

@@

We provide some analogies as to why cooperation does not imply authority. Object o can have the reference(capability) of o$'$, and hence there is cooperation, but o contains no methods that can invoke(use) the capability of o$'$, and thus o has the capability of o$'$ but not the authority of o$'$. Another analogy, from the other viewpoint of o$'$, would be that o$'$ has no available methods that can be invoked by o ---this can happen if o$'$ has no methods, or o$'$ only contains private methods or methods that are restricted for objects inherited from the same class as o$'$ of which o is not.\\

@@

This says that if we have a configuration where object o$'$ is dominated by trusted objects, then the permission to use o$'$ by o* must involve at least a trusted object s$'$. Therefore we can allow cooperation between o* and o$'$, and still make it safe by using an attenuating trusted object to \textit{shift the vulnerability} from the object of interest o$'$ to the attenuating trusted object. This shows that we can use attenuating objects to implement cooperation without vulnerability (of the object of interest) in OCap systems.\\
